Fisheries management when quotas are costly to change

### 2014-07-30 manuscripts/presentation.Rmd

---
title: "Fisheries management when quotas are costly to change"
date: "08/12/2014"
output: 
  ioslides_presentation:
    self_contained: false
    css: components/style.css
    incremental: true
transition: none
author: |
        Carl Boettiger, Michael Bode, James Sanchirico, 
        Jacob LaRiviera, Alan Hastings, Paul Armsworth

@@

theme_set(theme_tufte(base_size=18))
```
```{r analysis, include=FALSE}
source("components/analysis.R")
```

@@

![](components/images/tuna_cc0.jpg)

>>>>

---
title: "Fisheries management when quotas are costly to change"
date: "08/12/2014"
output: 
  revealjs_presentation:
    theme: serif
    self_contained: false
    incremental: true
    transition: none
    pandoc_args: ["--css", "components/style.css"]
author: Carl Boettiger, Michael Bode, James Sanchirico, Jacob LaRiviera, Alan Hastings, Paul Armsworth

@@

theme_set(theme_bw(base_size=18))
```
```{r analysis, include=FALSE}
source("components/analysis.R")
```

@@

![](components/images/tuna_cc0.png)
